---
title: "How Much of the World Has Access to the Internet ?"
output: pdf_document
---

\includegraphics{1.jpg}


# This report presents the state of internet accessibility across the world by answering these specific questions:

1. What are the top 5 countries with the highest internet use in 2019?
2. How many people had internet access in those countries in 2019?
3. What are the top 5 countries with the highest internet use for each of the following              regions: Middle East & North Africa, Latin America & Caribbean, East Asia & Pacific,              Europe & Central Asia?
4. Creating a visualization for those four regions.
5. What is the correlation between internet usage (population share) and broadband                   subscriptions in 2019?
6. Summarize my findings




# The data


#### internet
- "Entity" - The name of the country, region, or group.
- "Code" - Unique id for the country (null for other entities).
- "Year" - Year from 1990 to 2019.
- "Internet_usage" -  The share of the entity's population who have used the internet in the last three months.

#### people
- "Entity" - The name of the country, region, or group.
- "Code" - Unique id for the country (null for other entities).
- "Year" - Year from 1990 to 2020.
- "Users" - The number of people who have used the internet in the last three months for that country, region, or group.

#### broadband
- "Entity" - The name of the country, region, or group.
- "Code" - Unique id for the country (null for other entities).
- "Year" - Year from 1998 to 2020.
- "Broadband_Subscriptions" - The number of fixed subscriptions to high-speed internet at downstream speeds >= 256 kbit/s for that country, region, or group.



```{r, warning=FALSE,message=FALSE}

library(readr)
library(dplyr)
library(DescTools)
library(patchwork)
library(tidyr)
library(ggplot2)
library(scales)
library(stats)


internet <- read_csv("data/internet.csv")%>%
            distinct()%>%
            drop_na()

people  <- read_csv("data/people.csv")%>%
           distinct()%>%
           drop_na()


broadband <- read_csv("data/broadband.csv")%>%
             distinct()%>%
             drop_na()

```






## 1. What are the top 5 countries with the highest internet use in 2019?

```{r, warning=FALSE,message=FALSE}
  countries_with_highest_use <- internet%>%
                                group_by( Entity )%>%
                                filter( Year == 2019 )%>%
                                arrange( desc( Internet_Usage ) )%>%
                                mutate( Internet_Usage = paste( round( Internet_Usage, 
                                        2 ),"%" ), Year = Year )%>%
                                head(5)%>%
                                select(-Code,-Year)
  
  countries_with_highest_use

```




## 2. How many people had internet access in those countries in 2019?
```{r, warning=FALSE,message=FALSE}
    num_of_people <- people%>% 
                     filter( Year == 2019, Entity %in% 
                             countries_with_highest_use$Entity )%>%
                     arrange( desc( Users ) )%>%
                     select(-Code,-Year)

    num_of_people

    
    
    inner_join( countries_with_highest_use ,num_of_people , by=c( "Entity" ) )%>%
    arrange( desc( Users ) )
```

## 3. What are the top 5 countries with the highest internet use for each of the following regions: Middle East & North Africa,Latin America & Caribbean, East Asia & Pacific, Europe & Central Asia?
    
```{r, warning=FALSE,message=FALSE}
   our_regions <- c( 'Middle East & North Africa', 'Latin America & Caribbean',
                      'East Asia & Pacific', 'Europe & Central Asia' )
    regions <- d.countries%>%
               select( a3, region )%>%
               filter( region %in%  our_regions ) 

    internet_with_regions <- inner_join( internet, regions, by = c( "Code" = "a3" ) )
    
    
    
    #Middle East & North Africa
    top_Africa <- internet_with_regions%>%
                  filter( region == "Middle East & North Africa", Year == 2019 )%>%
                  arrange( desc( Internet_Usage ) )%>%
                  head(5)
    
    top_Africa   
    
    
    #Latin America & Caribbean
    
    top_Latin_America <- internet_with_regions%>%
                         filter( region == 'Latin America & Caribbean', Year == 2019 )%>%
                         arrange( desc( Internet_Usage ) )%>%
                         head(5)
    
    top_Latin_America
    
    #East Asia & Pacific
    top_East_Asia <- internet_with_regions%>%
                     filter( region == 'East Asia & Pacific', Year == 2019 )%>%
                     arrange( desc( Internet_Usage ) )%>%
                     head(5)
    
    top_East_Asia
    

  
    
    #'Europe & Central Asia'
    
    top_Europe_Central_Asia <- internet_with_regions%>%
                               filter( region == 'Europe & Central Asia', Year == 2019 )%>%      
                               arrange( desc( Internet_Usage ) )%>%
                               head(5)
    
    top_Europe_Central_Asia

```

## 4. Creating a visualization for those four regions

```{r, warning=FALSE,message=FALSE}
 A <- internet_with_regions%>%
      filter( Entity %in% top_Africa$Entity )%>%
      ggplot( aes( Year, Internet_Usage, group=Entity, color=Entity ) )+geom_line()+
      ggtitle("Internet usage over time Latin America & Caribbean")
    
    
  B <- internet_with_regions%>%
       filter( Entity %in% top_Latin_America$Entity )%>%
       ggplot( aes( Year, Internet_Usage, group=Entity, color=Entity ) )+geom_line()+
       ggtitle( "Internet usage over time Middle East & North Africa" )
    
    
  C <- internet_with_regions%>%
       filter( Entity %in% top_Europe_Central_Asia$Entity )%>%
       ggplot( aes( Year, Internet_Usage, group=Entity, color=Entity ) )+geom_line()+
       ggtitle( "Internet usage over time Europe & Central Asia" )
    
    
  D <- internet_with_regions%>%
       filter( Entity %in% top_East_Asia$Entity )%>%
       ggplot( aes( Year, Internet_Usage, group=Entity, color=Entity ) )+geom_line()+
       ggtitle( "Internet usage over time East Asia & Pacific" )
    
    
    A+B+C+D

```

## 5. What is the correlation between internet usage and broadband  subscriptions in 2019?


```{r, warning=FALSE,message=FALSE}
    internet_with_broadband<-internet%>%
                             filter(Year == 2019)%>%
                             inner_join( broadband, by = c("Entity","Year"),
                             suffix = c( "_internet", "_broadband" ) )
    cor.test( internet_with_broadband$Internet_Usage, 
        internet_with_broadband$Broadband_Subscriptions )
    
    ggplot(internet_with_broadband,aes( Internet_Usage, Broadband_Subscriptions,
    size = Internet_Usage ) )+geom_point( alpha = 0.8, color = "lightblue" )+
    ggtitle("Correlation between internet usage and broadband subscriptions in 2019")
 
```

&nbsp;                                                                                                                                                           

## 6. Summarize my findings

### The top 5 countries with the highest internet use were:
1. United Arab Emirates 99.15 percent of Internet use and 9133361 users
2. Denmark 98.05 percent of Internet use and 5682653 users
3. Kuwait 99.54 percent of Internet use and 4420795 users
4. Qatar 99.65 percent of Internet use and 2797495 users
5. Bahrain 99.7 percent of Internet use and 148973 users
   
   
### The top 5 countries with the highest internet use:
- **Middle East & North Africa**: Bahrain, Qatar, Kuwait, United Arab Emirates,  Saudi Arabia
- **Latin America & Caribbean**: Costa Rica, Uruguay, Puerto Rico, Mexico, Paraguay
- **East Asia & Pacific**: South Korea, Brunei, Hong Kong, Singapore, Macao
- **Europe & Central Asia**: Denmark, Norway, Sweden, Netherlands, Switzerlands


### The correlation between internet usage and broadband  subscriptions in 2019
  Correlation coefficient between internet usage and broadband  subscriptions is ***0.5575181***, which suggests a moderate   positive correlation between the variables.
    
  The ***t-value of 5.4971 with 67 degrees of freedom*** indicates a strong difference between the actual and theoretical correlation, and the very small ***p-value of 6.487e-07*** suggests that this difference is highly unlikely to be due to chance.
  
  At ***0.05 level of significance, we reject the null hypothesis***, which states that the true correlation between them is equal to 0.
  
  





